---
title: "20220607-Pride_Donations-Process"
author: "Kristen A, kkakey"
date: "6/22/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This Rmarkdown includes code and thoughts of my TidyTuesday process for 20220607! I don't include all the code I used, since this process is very iterative, but 5 general visualization stages for this week's TT.

This is for the NYC R-Ladies Code-laboration event https://www.meetup.com/rladies-newyork/events/286558385/

*********************************************

Example TidyTuesdays (with code) for this week:

- @issa_madjid https://twitter.com/issa_madjid/status/1534268235780063235
- @XuehuaiH https://twitter.com/XuehuaiH/status/1534331511532421121
- @danoehm https://twitter.com/danoehm/status/1535051951750414336


*********************************************

```{r}
library(ggplot2)
library(dplyr)
```

```{r}
pride_aggregates <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-06-07/pride_aggregates.csv')
fortune_aggregates <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-06-07/fortune_aggregates.csv')
static_list <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-06-07/static_list.csv')
pride_sponsors <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-06-07/pride_sponsors.csv')
corp_by_politician <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-06-07/corp_by_politician.csv')
donors <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-06-07/donors.csv')
```

**exploratory data analysis**

- What data is available? 
- What questions can you ask with the data available? 
- What are some interesting trends?


note: I didn't include all my code chunks exploring the various datasets, but that's where I always start!

What I decided to look at: Pride sponsors who have donated to Anti-LQBTQ Campaigns
```{r}
static_list %>%
  filter(`Pride?`==TRUE) #%>%
  # summarize(quantile(`Amount Contributed Across States`))
```


```{r}
### Sum of donations contributed to anti-LBGTQ politicians by pride sponsors
pride_aggregates %>%
  filter(Company=="Grand Total")
```


*********************************************

- "Circular packing or circular treemap allows to visualize a hierarchic organization. It is an equivalent of a treemap or a dendrogram, where each node of the tree is represented as a circle and its sub-nodes are represented as circles inside of it." (https://r-graph-gallery.com/circle-packing.html)
- "A Treemap displays hierarchical data as a set of nested rectangles. Each group is represented by a rectangle, which area is proportional to its value." (https://r-graph-gallery.com/treemap.html)

```{r}
## https://r-graph-gallery.com/circle-packing.html
## https://r-graph-gallery.com/305-basic-circle-packing-with-one-level.html
install.packages('packcircles')
library(packcircles)
```


```{r}
set.seed(99)
anti_lgbt <- static_list %>%
  filter(`Pride?`==TRUE) %>%
  # randomly reorder columns
  .[sample(1:nrow(.)), ]

packing <- circleProgressiveLayout(anti_lgbt$`Amount Contributed Across States`, sizetype='area')
packing$radius <- 0.95*packing$radius # adds space around circles
anti_lgbt <- cbind(anti_lgbt, packing)
anti_lgbt.gg <- circleLayoutVertices(packing, npoints=500)
```

```{r}
# modify text in circles 
anti_lgbt <- anti_lgbt %>%
  mutate(text = paste0(Company, '\n', "$", scales::comma(`Amount Contributed Across States`)))
```

```{r}
ggplot() + 
  
  # Make the bubbles
  geom_polygon(data = anti_lgbt.gg, aes(x, y, group = id, fill=as.factor(id)), colour = "black", alpha = 0.6) +
  
  # Add text in the center of each bubble + control its size
  geom_text(data = anti_lgbt, aes(x, y, size=`Amount Contributed Across States`/2, label = text)) +
  scale_size_continuous(range = c(2,5)) +
  
  # General theme:
  # theme_void() + 
  theme(legend.position="none") +
  coord_equal() 

ggsave("test1.png")
```



****************

```{r}
anti_lgbt <- static_list %>%
  filter(`Pride?`==TRUE) 

packing <- circleProgressiveLayout(anti_lgbt$`Amount Contributed Across States`, sizetype='area')
packing$radius <- 0.9*packing$radius 
anti_lgbt <- cbind(anti_lgbt, packing)
anti_lgbt.gg <- circleLayoutVertices(packing, npoints=20)
```

```{r}
anti_lgbt <- anti_lgbt %>%
  mutate(
     id = row_number(),
     text = paste0(Company, '\n', "$", scales::comma(`Amount Contributed Across States`))
  )
```

```{r}
ggplot() + 
  
  # Make the bubbles
  geom_polygon(data = anti_lgbt.gg, aes(x, y, group = id, fill=as.factor(id)), colour = "black", alpha = 0.6) +
  
  # Add text in the center of each bubble + control its size
  geom_text(data = anti_lgbt, aes(x, y, size=`Amount Contributed Across States`, label = text), 
            family = "Open Sans") +
  scale_size_continuous(range = c(2,5)) +
  
  # General theme:
  theme_void() + 
  theme(legend.position="none") +
  coord_equal() 


ggsave("test3.png")
```


****************

```{r}
anti_lgbt <- static_list %>%
  filter(`Pride?`==TRUE) 

packing <- circleProgressiveLayout(anti_lgbt$`Amount Contributed Across States`, sizetype='area')
packing$radius <- 0.9*packing$radius # adds space around circles
anti_lgbt <- cbind(anti_lgbt, packing)
## increase the circle resolution
anti_lgbt.gg <- circleLayoutVertices(packing, npoints=700)
```

```{r}
anti_lgbt <- anti_lgbt %>%
  mutate(
     id = row_number(),
     text = paste0(stringr::str_wrap(Company,12), '\n', "$", scales::comma(`Amount Contributed Across States`)),
     ## change the fill color
     fill_col = rainbow(30)
  )

anti_lgbt.gg <- anti_lgbt.gg %>%
  left_join(., anti_lgbt %>% select(!c(x,y)), by = "id")
```


```{r}
ggplot() + 
  geom_polygon(data = anti_lgbt.gg, aes(x, y, group = id, fill=as.factor(fill_col)), colour = "black", alpha = 0.6) +
  scale_fill_identity() +
  ## don't include text for the smaller circles
  geom_text(data = anti_lgbt[anti_lgbt$`Amount Contributed Across States`>10000,], 
            aes(x, y, size=`Amount Contributed Across States`, label = text, lineheight = 1), 
            family = "Roboto", color = "white") +
  scale_size_continuous(range = c(2,5)) +
  theme_void() + 
  theme(legend.position="none") +
  coord_equal() 


ggsave("test4.png")
```


**************************************************

```{r}
ggplot() + 
  geom_polygon(data = anti_lgbt.gg, aes(x, y, group = id, fill=as.factor(fill_col)), 
               colour = "black", alpha = 0.6) +
  scale_fill_identity() +
  geom_text(data = anti_lgbt[anti_lgbt$`Amount Contributed Across States`>10000,], 
            aes(x, y, size=`Amount Contributed Across States`, label = text, lineheight = 1,
                family = "Roboto"), color = "white") +
  scale_size_continuous(range = c(1,4)) +
  theme_void() +
  theme(legend.position="none",
        panel.background = element_rect(fill="#36454F", color=NA),
        plot.background = element_rect(fill="#36454F", color=NA),
        plot.title = element_text(family = "JosefinSans-SemiBold", 
                                  color = "white", hjust=.5, #vjust=2.3,
                                  margin = margin(t = 10, b = 0, l = 0)),
        plot.caption = element_text(family = "JosefinSans-SemiBold", size = 3, color = "white",
                                    hjust=.99, vjust = 8)) +
  ggtitle("PRIDE SPONSORS\nWho Also Donated To\nANTI-LGBTQ CAMPAIGNS") +
  labs(caption = "Data: Data For Progress\nCreated by: @kkakey") +
  coord_equal() 

ggsave("test5.png", height = 5, width = 5, dpi = 300)
```



